Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-28 transmission.tex
add extra gof plots for ATACCC
add implementation details

@@

@@

\ifSubfilesClassLoaded{
  \appendix
  \subfile{transmission-appendix-INLA}
  \subfile{transmission-appendix-phase-type}
  \subfile{transmission-appendix-plots}
  \listoftodos
}{}

>>>>

The posterior samples of $\vec{P}$ are produced within the SRS and then extracted.
I implement the calculation of $\vec{Z}$ and poststratification in R~4.2.0~\autocite{R-4-2-0} using the built in \texttt{forwardsolve} function, tidybayes~3.0.6~\autocite{tidybayes}, and the tidyverse set of packages~\autocite{tidyverse}.

@@

\subsubsection{Implementation}

I implemented the simulations study and inference code in Python~3.8.2~\autocite{python} using pandas~2.0.3~\autocite{pandas}, numpy~1.24.4~\autocite{numpy}, and scipy~1.10.1~\autocite{scipy}.
The strata are larger than those in \cref{backcalc}, allowing the data to be extracted from the SRS.
Therefore, inference was performed using the University of Cambridge high-performance cluster.

@@

\ifSubfilesClassLoaded{
  \appendix
  \subfile{transmission-appendix-INLA}
  \subfile{transmission-appendix-phase-type}
  \subfile{appendix-plots}
  \listoftodos
}{}
